Regularising Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable

### 2022-03-20 article.rnw
Remove an unnecessary sentence.
I don't think using the word "regularising" is helping much.
Apart from this sentence to explain what it is,
which doesn't mesh well with the paragraph it begins,
the word is only used in the title.
I think we're best off rewording the title and avoiding the word "regularising".

%Title Page
\title{Regularising Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable}
\author{Christopher R.\ P.\ Brown}
\author{Daniel B.\ Stouffer}
\affil{Centre for Integrative Ecology, School of Biological Sciences, University of Canterbury, Christchurch, New Zealand}
\date{}

@@

In the statistical literature, regularisation is the process of using external information to prevent overfitting or to solve an otherwise overspecified problem \parencite{XXX}.
One simplifying approach is to assume that most pairs of species do not interact or interact weakly, and hence setting many of the parameters to zero \parencite{XXX}. %TODO: XXX why this could be a problem XXX.
Alternatively, one can assume that species fall into groups, such that all species in the same group interact with species in other groups in an identical fashion, thereby collapsing pairwise interaction parameters for all the species in that group into sets of common parameters \parencite{ovaskainen2017species,weiss2021disentangling}.

>>>>

%Title Page
\title{Regularising Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable} %TODO: Remove the word "regularising" from the title.
\author{Christopher R.\ P.\ Brown}
\author{Daniel B.\ Stouffer}
\affil{Centre for Integrative Ecology, School of Biological Sciences, University of Canterbury, Christchurch, New Zealand}
\date{}

@@

One simplifying approach is to assume that most pairs of species do not interact or interact weakly, and hence setting many of the parameters to zero \parencite{XXX}. %TODO: XXX why this could be a problem XXX.
Alternatively, one can assume that species fall into groups, such that all species in the same group interact with species in other groups in an identical fashion, thereby collapsing pairwise interaction parameters for all the species in that group into sets of common parameters \parencite{ovaskainen2017species,weiss2021disentangling}.
